Mechanism to control synchronization in coupled area-preserving maps

### 2018-08-29 Syncarea_control/paper.tex
paper updated

\begin{abstract}
A unidirectionally coupled area-preserving maps with mixed phase space may identical synchronization in the sticky neighborhood of the regular islands. We use this fact to devise numerical procedures to delay and advance the process of synchronization. The delay method is based on controlled kicking of the trajectories away from the regular islands for as long as required. The method to expedite the process is achieved by a parameter perturbation technique which rapidly drives the chaotic trajectories in the neighborhood of regular islands where synchronization occurs. We also point out the limitations of these methods.   
\end{abstract}

>>>>

\begin{abstract}
 A unidirectionally coupled area-preserving maps with mixed phase space may 
show identical synchronization in the sticky neighborhood of the regular 
islands. We use this fact to devise a couple of numerical procedures to 
delay and expedite the process of synchronization in standard maps coupled 
under  Pecora-Caroll scheme. The delay method is based on controlled 
kicking of trajectories away from the regular islands for as long as 
necessary. On the other hand, the method to expiate the process is
achieved by a parameter perturbation technique which rapidly drives the 
chaotic trajectories to synchronization traps in the sticky neighborhoods 
of regular islands. We also point out of limitations of these methods.  
\end{abstract}
